### 2020-02-05 README.Rmd
[docs] Rename project-wide
# |<----  Using a Maximum Of 50 Characters  ---->|


# Explain why this change is being made
# |<----   Try To Limit Each Line to a Maximum Of 72 Characters   ---->|

# Provide links or keys to any relevant tickets, articles or other resources
# Example: Github issue #23

# --- COMMIT END ---
# Type can be 
#    feat (new feature)
#    fix (bug fix)
#    docs (changes to documentation)
#    style (formatting, missing semi colons, etc; no code change)
#    refactor (refactoring production code)
#    test (adding missing tests, refactoring tests; no production code cha

# Please put your title here to include it in the file below.
Title <- "Resilience of different technologies towards climate change for Singapore"
```

# resilience

<!-- badges: start -->
[![R build status](https://github.com/ideas-lab-nus/resilience/workflows/build-paper/badge.svg)](https://github.com/ideas-lab-nus/resilience/actions)
<!-- badges: end -->

@@

You can download the compendium as a zip from from this URL:
<https://github.com/ideas-lab-nus/resilience/archive/master.zip>

Or you can install this compendium as an R package, resilience, from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("ideas-lab-nus/resilience")
```

>>>>

# Please put your title here to include it in the file below.
Title <- "An R-based framework for conducting parametric analysis on building energy models"
```

# eplusr + epluspar

<!-- badges: start -->
[![R build status](https://github.com/ideas-lab-nus/epluspar-paper/workflows/build-paper/badge.svg)](https://github.com/ideas-lab-nus/epluspar-paper/actions)
<!-- badges: end -->

@@

You can download the compendium as a zip from from this URL:
<https://github.com/ideas-lab-nus/epluspar-paper/archive/master.zip>

Or you can install this compendium as an R package, epluspar-paper, from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("ideas-lab-nus/epluspar-paper")
```
